Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-13 paper/structureScene.tex
Edit filter bank phrase

Scattering transforms are time-shift invariant representations of audio signals consisting of auditory and modulation filter banks alternated with complex modulus non-linearities.
This section first explains the importance of local invariance to time-shifting and stability to time-warping in the representation of acoustic scenes, then describes how the scattering transform is designed to satisfy these properties while having a high discriminative power.

>>>>

Scattering transforms are time-shift invariant representations of audio signals computed by applying auditory and modulation filter banks alternated with complex modulus non-linearities.
This section first explains the importance of local invariance to time-shifting and stability to time-warping in the representation of acoustic scenes, then describes how the scattering transform is designed to satisfy these properties while having a high discriminative power.
